A Data-Driven Framework for Neural Field Modelling

### 2010-10-29 ltx/first_order_framework/LaTeX_Manuscript.tex
Changed Figure4

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure4.pdf}
\end{center}
\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
\label{fig:Figure4}
\end{figure}

>>>>

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure4.pdf}
\end{center}
\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{a}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{b}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
\label{fig:Figure4}
\end{figure}
